---
title: "Gaze-xsit Models"
author: "Kyle MacDonald"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Model 

Question: For each condition, does the amount of time looking at the object during exposure trials predict
the participants' success (higher accuracy) on test trials? 

Define Same and Switch trials are inferred based on participant looking during exposure trials. 

* Same trials are... 
* Switch trials are...

Predictions: 

* In the gaze condition, participants will allocate more attention to the target of gaze, and thus perform at chance on 
"Switch" test trials where the target of gaze is not present. 
* In the no-gaze condition, participants will allocate equal attention to both objects on exposure trials, and thus perform better on 
"Switch" test trials.
* A quantiative relation between the amount of looking during exposure and the success at test. [allocation of attention model]
* When gaze and no-gaze participants allocate the same amount of attention during exposure, gaze participants will still perform 
worse that no gaze participants on "Switch" Trials. [social is special model]

Models:

  1) Predicting looking behavior (proportion correct or proportion looking to the kept object) based on condition 
  2) Predicting looking behavior based on trial type (Same/Switch binned based on looking behavior during exposure trials)

```{r}
m1.cont <- lmer(test ~ exposure * condition + (1|subid), 
                data = filter(ss_acc_all, is.na(exposure) == F))
kable(summary(m1.cont)$coef)
```

Categorical model with exposure looking binned into 4 groups.

```{r}
m2.cat <- lmer(test ~ exptarget_bin * condition + (1|subid), data = ss_acc_all) 
kable(summary(m2.cat)$coef)
```
