---
title: "Gaze-xsit Timecourse"
author: "Kyle MacDonald"
output: html_document
---

```{r chunk opts}
rm(list = ls())
knitr::opts_chunk$set(echo=T, warning=F, cache=F, message=F, sanitize = T)
source("../helper_functions/helper_functions.R")
```

This script munges and analyzes the data for a project exploring the association between allocation of attention and cross-situational word learning in more or less ambiguous contexts.

Read data.

```{r}
d <- read_csv("../../data/3_tidy_data/gaze_xsit_tidy_trial_level.csv")
d_time <- read_csv("../../data/3_tidy_data/gaze_xsit_tidy_timecourse.csv")
```

## Diagnostic plots

Here, we create some plots to check the quality of eye tracking data. 

```{r}
d_plot <- d_time %>%
  filter(trial_num != "fam", !is.na(x), !is.na(y)) %>%
  mutate(x = ifelse(x < 1 | x > 1919, NA, x), 
         y = ifelse(y < 1 | y > 1079, NA, y))
```

```{r, fig.height=10, fig.width=10}
d_plot %>% 
  filter(subid == subid[22]) %>% 
  ggplot(aes(x = t.stim, y = x)) + 
  geom_line(col = "darkgrey") + 
  geom_point(aes(col = ss_looking_char), alpha = .3) + 
  facet_wrap(~trial_num*trial.type, ncol = 8) + 
  ylim(c(0,1920)) + 
  geom_hline(yintercept = 1920/2, lty = 2) +
  theme(legend.position = "top")
```

```{r, fig.height=8, fig.width=12}
d_plot %>% 
  filter(subid == subid[22]) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_line(col = "darkgrey") + 
  geom_point(aes(col = ss_looking_char), alpha = .3) + 
  facet_wrap(~trial_num*trial.type, ncol = 8) + 
  xlim(c(0,1920)) + 
  ylim(c(0,1080)) +
  theme(legend.position = "top")
```

## Timecourse plot

```{r}
d.filt <- d_time %>% filter(t.stim >= 0, t.stim <= 4,
                            trial_num != "fam", trial.type != "familiar",
                            ss_looking_char %in% c("left", "right", "face"))
```

First, we generate curves that represent center, target, and distractor looking over time

Summarize data for each ROI for each participant and each time slice.

```{r}
# get count of looking to each picture
ss <- d.filt %>% 
  group_by(subid, t.stim, condition, correct_char, trial.type) %>% 
  summarise(count_looks = n()) 

# complete the cases 
# this takes care of when there was no looking to one of the images
ss %<>% 
  ungroup() %>% 
  complete(subid, t.stim, correct_char, trial.type,
           fill = list(count_looks = 0)) %>%
  arrange(subid)

# get the total number of time slices for each trial and
ss %<>% 
  group_by(subid, t.stim, trial.type) %>% 
  mutate(total_looks = sum(count_looks)) %>% 
  filter(total_looks > 0) # remove trials without any looking data

# get proportion looking to face and objects during each trial
ss %<>% mutate(prop_looking = round(count_looks / total_looks, 2))
```

Get means and CIs for proportion looking at each time slice across particpants

```{r}
ms.means.timeslice <- ss %>% 
  filter(is.na(condition) == F) %>% 
  group_by(t.stim, condition, correct_char, trial.type) %>% 
  summarise(mean = mean(prop_looking, na.rm = T))
```

Now make the Tanenhaus style curves for each type of looking.  

```{r}
ms.means.timeslice %>% 
  filter(t.stim <= 4) %>% 
  ggplot(aes(x = as.numeric(t.stim), y = mean, 
             color = condition), data = .) + 
  ylim(0,0.75) +
  xlim(0,5) +
  geom_line(size=1) +
  guides(color = F) +
  xlab("Time in sec from onset of trial") +
  ylab("Proportion looking") +
  geom_dl(aes(label = condition), method = "last.bumpup") +
  theme(legend.position = "top") +
  facet_grid(correct_char~trial.type)
```